Appendix 4: Model Comparison Code For Manuscript

### 2025-10-30 modelcomparison_code.Rmd
adding de01 and de02 back into model
Editing figure

#regression
ss_intention ~  cp * ss_donation + b1 * ss_psycown + b2 * ss_selfid

@@

@@

pf <- data.forest %>% 
  ggplot(aes(est,xmin=ci.lower,xmax=ci.upper,y=term,fill=hollow_group,color=color,linetype=linetype))+
  geom_vline(xintercept=0,color="grey") +
  geom_linerange(position=pos)+
  geom_point(aes(shape = sample),size=3,position=pos,alpha=0.7)+
  scale_fill_discrete(na.value=NA, guide ="none") + 
  labs(x="Standardised effect size",y="Relationship") +
  labs(shape="Sample", color="Model type", linetype="Variable type") +
  geom_stripped_rows(color=NA) + theme_classic()

>>>>

#regression
ss_intention ~  de01 + de02 + cp * ss_donation + b1 * ss_psycown + b2 * ss_selfid

@@

```
```{r}
lavaan::inspect(fit.po03ss,"r2")
```

@@

pf <- data.forest %>% 
  ggplot(aes(est,xmin=ci.lower,xmax=ci.upper,y=term,fill=hollow_group,color=color,linetype=linetype))+
  geom_vline(xintercept=0,color="grey") +
  geom_linerange(aes(size = sample), position=pos) +
  scale_size_manual(values = c("Australia" = 1.2, "Finland" = 0.8)) +
  geom_point(aes(shape = sample),size=3,position=pos,alpha=0.7)+
  scale_fill_discrete(na.value=NA, guide ="none") + 
  labs(x="Standardised Effect Size",y="Relationship") +
  labs(color="Model type", linetype="Variable type", shape="Sample") + 
  guides(size = "none") +
  geom_stripped_rows(color=NA) + theme_classic()
